%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Ericsson}{Sept 2024 - Present}
    {Full-Stack Android Developer Part-Time}{Remote}
     \resumeItemListStart
       \resumeItem{Split responsibilities between \textbf{EIP FE} development and Android development for the \textbf{Ericsson 5G Scanner project}.}
       \resumeItemListEnd
    \resumeSubheading
    {Ericsson}{May 2023 - Aug 2024}
    {Full-Stack Android Developer Intern}{Ottawa, ON, Hybrid}
    \resumeItemListStart
       \resumeItem{Led a team of 2 interns in the design and development of \textbf{Ericsson’s 5G Rapid Scanner Android app} for real-time 5G NR / 4G LTE network analysis. Utilized \textbf{Jira} and \textbf{Gerrit} to manage tasks and workflow in accelerated Agile sprints.}
       \resumeItem{Integrated {\textbf{SSO}} authentication via {\textbf{MSAL}} and {\textbf{Azure}}, securing access for {\textbf{100,000+ internal users}}..} 
       \resumeItem{Enhanced {\textbf{UX}} with dynamic themes, and integrated \textbf{Mapbox API} for real-time geographic tracking and scanning.} 
       \resumeItem{Implemented {\textbf{iPerf3}} servers for throughput testing over \textbf{Azure} for internal access, and optimized scan history search with {\textbf{incremental loading}}, reducing search and loading times by over {\textbf{90\%}}.} 
       \resumeItem{Built the app with {\textbf{React Native}} and {\textbf{Typescript}} front-end, using {\textbf{Java}} for security encryption and root detection, and {\textbf{C++/ASP.NET}} for backend iPerf libraries.  Utilized \textbf{React Native Metro}  and \textbf{Android Studio} for development.} 
       \resumeItem{Applied Web application technologies as part of the Front-End team, utilizing \textbf{HTML5}, \textbf{Typescript}, \textbf{React} and \textbf{Redux}.} 
       \resumeItemListEnd

 

    \resumeSubheading
    {Ross Video}{May 2022 - Aug 2023}
    {Software Developer Intern}{Ottawa, ON}
    \resumeItemListStart
        \resumeItem{Developed automated test software in \textbf{Python} into verify the integrity of Ross products, working closely with automation developers, verification specialists, and product developers as part of the SoftGear Team. }
        \resumeItem{Implemented \textbf{Python-based automation scripts} and created a network-connected GUI using \textbf{QT}, improving testing efficiency for Ross hardware by \textbf{80\%} over the course of a year. }
        \resumeItem{Contributed to the company's internal \textbf{automation library}, extending its use across multiple projects. }
    \resumeItemListEnd

\resumeSubheading
    {Digibiomics}{May 2021 - Aug 2021}
    {Junior Web Developer Intern}{Ottawa, ON}
    \resumeItemListStart
        \resumeItem{Developed "MyHealthyHost" e-commerce platform using \textbf{HTML}, \textbf{React}, \textbf{CSS}, \textbf{Bootstrap}, and \textbf{JQuery}.   }
        \resumeItem{Implemented \textbf{PHP} form submissions and launched the platform on \textbf{AWS.}}
    \resumeItemListEnd
    
\resumeSubHeadingListEnd